SMT-Boosted Security Types for Low-Level MPC

### 2025-11-07 toplas26/sty.tex
checkpoint

\subsection{Share Typing Example} To illustrate details of the
type system we return to the example of additive sharing in the context
of a 2-client protocol. We first focus on initial secret sharing steps--
let $\prog$ be the following protocol in $\fieldp{2}$ (noting
that $-$ is equivalent to xor in $\fieldp{2}$):
$$
\begin{array}{lll}
  \elab{\mesg{s1}}{2} &:=& \elab{(\secret{1} \fminus \locflip)}{1}; \\
  \elab{\mesg{s2}}{1} &:=& \elab{(\secret{2} \fminus \locflip)}{2} 
\end{array}
$$
We can then assert:
$$
\toeq{\prog} \vdash \varnothing,\varnothing \stredx
\setit{[\mx{s2}{1}, \elab{\locflip}{2}] : \sharety,
  [\mx{s1}{2}, \elab{\locflip}{1}] : \sharety}, \setit{\elab{\locflip}{1},\elab{\locflip}{2}}
$$
Suppose the protocol goes on to reveal the negation of the
sum (xor-ing) of the inputs:
$$
\begin{array}{lll}
  \px{1} &:=& \elab{\mesg{s2} + \locflip + 1}{1}; \\
  \px{2} &:=& \elab{\mesg{s1} + \locflip}{2}\\
  \out{1} &:=& \elab{\px{1} + \px{2}}{1}\\
  \out{2} &:=& \elab{\px{1} + \px{2}}{2}
\end{array}
$$
Letting this extended protocol be $\prog'$, and letting:
$$
\begin{array}{rcl}
\Gamma &\defeq& \setit{[\mx{s2}{1}, \elab{\locflip}{2}] : \sharety,
  [\mx{s1}{2}, \elab{\locflip}{1}] : \sharety}\\
R &\defeq&  \setit{\elab{\locflip}{1},\elab{\locflip}{2}}
\end{array}
$$
observe we can then obtain share typings for noninteractive components for
addition of shares by \TirName{Shared} and \TirName{HeAdd}:
$$
\Gamma, \toeq{\prog'} \vdash
[\mx{s2}{1} + \elab{\locflip}{1}, \mx{s1}{2} + \elab{\locflip}{2}] : \sharety
$$
and hence for negation by \TirName{HeAddPub}:
$$
\Gamma, \toeq{\prog'} \vdash
[\mx{s2}{1} + \elab{\locflip}{1} + 1, \mx{s1}{2} + \elab{\locflip}{2}] : \sharety
$$
This implies:
$$
\toeq{\prog'} \vdash \varnothing,\varnothing \stredx
\Gamma \cup \setit{\pubx{\px{1} + \px{2}} : \outty}, R 
$$
Hence by \TirName{PubEntails} we have:
$$
\begin{array}{l}
\Gamma \cup \setit{\pubx{\px{1} + \px{2}} : \outty}, \toeq{\prog'} \vdash
\pubx{\out{1}} : \outty \\
\Gamma \cup \setit{\pubx{\px{1} + \px{2}} : \outty}, \toeq{\prog'} \vdash
\pubx{\out{2}} : \outty
\end{array}
$$

@@

\begin{definition}
  We write $\eqs,\Gamma,R : {OK}$ iff both of the following conditions hold:
  \begin{enumerate}[\hspace{5mm}i.]
  \item For all $([\mx{z}{\cid}, \rx{y}{\cid'}] : \sharety) \in \Gamma$,
    we have $\eqs \models \mx{z}{\cid} \eop \phi - \rx{x}{\cid'}$ for
    some $\phi$ and unique $\rx{x}{\cid'} \in R$, with $\cid \ne \cid'$.
  \item For all $([\phi] : \pubty) \in \Gamma$,
    we have $\eqs \models \phi \eop \phi' - \rx{x}{\oid}$ for
    some $\phi'$ and unique $\rx{x}{\oid} \in R$.
  \end{enumerate}
\end{definition}

@@

\begin{lemma}
  Assume given $\Gamma,R, \eqspre \wedge \toeq{\prog} : {OK}_\cid$  and
  $\iov(\prog) = S \cup V \cup O$
  and $\Gamma, \eqspre \wedge \toeq{\prog} \vdash [\phi_1,\phi_2] : \sharety$.
  Then, letting $X \defeq \ov(\Gamma) \cap \realviews{\setit{\cid_1}}{\setit{\cid_2}}$:
  $$
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}}  \cup X \cup \setit{\phi_1 + \phi_2}}
  = 
  \condd{\progtt(\prog)}{S_{\setit{\cid_1}}}{S_{\setit{\cid_2}} \cup X \cup \setit{\phi_1 + \phi_2, \phi_1}}
  $$
\end{lemma}

>>>>

We write $\stredx^*$ to denote the reflexive, transitive
closure of $\stredx$. For any protocol $\prog$, the goal of the
type analysis is to show that all interactive messages can be classified--
that is, to show that $\eqspre \wedge \toeq{\prog} \vdash
\varnothing,\varnothing \stredx^* \Gamma,R$ where all
interactive messages are classified in $\Gamma$.

\subsection{Share Typing Example} To illustrate details of the
type system we return to the example of additive sharing in the context
of a 2-client protocol. We first focus on initial secret sharing steps--
let $\prog$ be the following protocol in $\fieldp{2}$ (noting
that $-$ is equivalent to xor in $\fieldp{2}$):
$$
\begin{array}{lll}
  \elab{\mesg{s1}}{2} &:=& \elab{(\secret{1} \fminus \locflip)}{1}; \\
  \elab{\mesg{s2}}{1} &:=& \elab{(\secret{2} \fminus \locflip)}{2} 
\end{array}
$$
We can then assert:
$$
\toeq{\prog} \vdash \varnothing,\varnothing \stredx
\setit{[\mx{s2}{1}, \elab{\locflip}{2}] : \sharety,
  [\mx{s1}{2}, \elab{\locflip}{1}] : \sharety}, \setit{\elab{\locflip}{1},\elab{\locflip}{2}}
$$
Suppose the protocol goes on to reveal the negation of the
sum (xor-ing) of the inputs:
$$
\begin{array}{lll}
  \px{1} &:=& \elab{\mesg{s2} + \locflip + 1}{1}; \\
  \px{2} &:=& \elab{\mesg{s1} + \locflip}{2};\\
  \out{1} &:=& \elab{\px{1} + \px{2}}{1};\\
  \out{2} &:=& \elab{\px{1} + \px{2}}{2}
\end{array}
$$
Letting this extended protocol be $\prog'$, and letting:
$$
\begin{array}{rcl}
\Gamma &\defeq& \setit{[\mx{s2}{1}, \elab{\locflip}{2}] : \sharety,
  [\mx{s1}{2}, \elab{\locflip}{1}] : \sharety}\\
R &\defeq&  \setit{\elab{\locflip}{1},\elab{\locflip}{2}}
\end{array}
$$
observe we can then obtain share typings for noninteractive components for
addition of shares by \TirName{Shared} and \TirName{HeAdd}:
$$
\Gamma, \toeq{\prog'} \vdash
[\mx{s2}{1} + \elab{\locflip}{1}, \mx{s1}{2} + \elab{\locflip}{2}] : \sharety
$$
and hence for negation by \TirName{HeAddPub}:
$$
\Gamma, \toeq{\prog'} \vdash
[\mx{s2}{1} + \elab{\locflip}{1} + 1, \mx{s1}{2} + \elab{\locflip}{2}] : \sharety
$$
This implies:
$$
\toeq{\prog'} \vdash \varnothing,\varnothing \stredx
\Gamma \cup \setit{\pubx{\px{1} + \px{2}} : \outty}, R 
$$
Hence by \TirName{PubEntails} we have:
$$
\begin{array}{l}
\Gamma \cup \setit{\pubx{\px{1} + \px{2}} : \outty}, \toeq{\prog'} \vdash
\pubx{\out{1}} : \outty \\
\Gamma \cup \setit{\pubx{\px{1} + \px{2}} : \outty}, \toeq{\prog'} \vdash
\pubx{\out{2}} : \outty
\end{array}
$$

@@

Now we can prove our share typing soundness result, showing that share
typing enforces noninteference modulo output, with our main result
in Theorem \ref{theorem-sty}. We begin by defining a key well-formedness
property of typing components that we show is preserved by non-interactive
typing judgements.
\begin{definition}
  We write $\eqs,\Gamma,R : {OK}$ iff both of the following conditions hold:
  \begin{enumerate}[\hspace{5mm}i.]
  \item For all $([\mx{z}{\cid}, \rx{y}{\cid'}] : \sharety) \in \Gamma$,
    we have $\eqs \models \mx{z}{\cid} \eop \phi - \rx{x}{\cid'}$ for
    some $\phi$ and unique $\rx{x}{\cid'} \in R$, with $\cid \ne \cid'$.
  \item For all $([\phi] : \pubty) \in \Gamma$,
    we have $\eqs \models \phi \eop \phi' - \rx{x}{\oid}$ for
    some $\phi'$ and unique $\rx{x}{\oid} \in R$.
  \end{enumerate}
\end{definition}

@@
